Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-21 paper/paper.Rmd
simplify use of the Heavside step function closing #9

\begin{align*}
  r_0 &\sim \text{Normal}\left(0, 0.25 \right) \\
  r_t &= \left(\mathcal{H}(r_{t-1} > 0) \xi_{+} + \mathcal{H}(r_{t-1} \le 0) \xi_{-}\right)r_{t-1} + \epsilon_t  \\
  \epsilon_t &= \mathcal{H}(t > 0) \beta \epsilon_{t-1} + \eta_t
\end{align*}

Where $\mathcal{H}$ is the Heaviside step function and is defined such that it attains the value of 1 if the argument is true and the value of 0 otherwise, and $\epsilon_t$ and $\eta_t$ are error terms. 
The following priors are used,

>>>>

\begin{align*}
  r_0 &\sim \text{Normal}\left(0, 0.25 \right) \\
  r_t &= \left(\mathcal{H}(r_{t-1}) \xi_{+} + (1 - \mathcal{H}(r_{t-1})) \xi_{-}\right)r_{t-1} + \epsilon_t  \\
  \epsilon_t &= \mathcal{H}(t > 0) \beta \epsilon_{t-1} + \eta_t
\end{align*}

Where $\mathcal{H}(r_{t-1})$ is the Heaviside step function and is defined such that it attains the value of 1 if the argument is greater than 0 and 0 otherwise, and $\epsilon_t$ and $\eta_t$ are error terms. 
The following priors are used,
